---
title: "MDMA/Psychadelics multi-level meta analysis"
---

```{r load packages}
library(tidyverse)
library(here)
library(metafor)
library(dmetar)
```


```{r load data}

file_sources <- list.files(
  path = here::here("data"),
  pattern = "*.csv"
)

my_dat <- lapply(paste0(here::here("data"),"/", file_sources), read.csv)
my_dat <- lapply(my_dat, function(x){
  x %>%
    mutate(var_es = se_es^2) %>%
    mutate(es_sample = sample(seq(-3, 3, length.out = 1000), size = nrow(.)), replace = FALSE)
})
names(my_dat) <- file_sources
```

# Analysis
Manche Studien kommen doppelt vor, weil sie mit verschiedenen Tests eingehen. D.h. wir könnten jetzt Ein Studien-Cluster generieren. 

```{r}
## Beim einlesen von dat_1 ist irgendwas schief gegangen. 
model_1 <- rma.mv(yi = es_sample, # austauschen, aktuell gesampelt
                  V = var_es, 
                  slab = Study,
                  data = my_dat[[2]],
                  random = ~1|Study/es.id, #Nesting the effect size within the Studys
                  test = "t", 
                  method = "REML"
                  )

summary(model_1)
```

sigma^2.1 contains the level 3 between-cluster variance, which is the between-study heterogeneity variance. 
sigma^2.2 shows the variance within clusters (level 2).
estimate is our estimated pooled effect. How to interpret? I would need more information about the es. 
But how much heterogeneity variance is captured by each level of our model?
$I^2$ quantifies the amount of variation not attributable to sampling error. In three level models, it is split into a part attributable to true effect size differences within clusters (level 2) and between cluster variation (level 3). 
We have 2 $I^2$ quantifying the percentage of total variation associated with either level 2 or level 3. 

```{r}
i2 <- var.comp(model_1)
```
We get the percentages of variance explained by 
1) sampling error variance
2) heterogeneity variance within clusters
3) Between study heterogeneity percentage of total variation of the effect sizes. 

We can compare the three level model to a two level model: 



Currently we assume that within one study, effect size estimates are independent. -> maybe look at robust variance estimation 




