---
title: "MDMA/Psychadelics multi-level meta analysis"
author: Nicklas Hafiz
date: "`r format(Sys.time(), '%d %B, %Y')`"
format: 
  html:
    toc: true
    toc-depth: 4
    theme: sandstone
    embed-resources: true
    fig-width: 10
    fig-height: 8
bibliography:
  - grateful-refs.bib
  - references.bib
---

```{r load packages}
#| warning: false
#| message: false
#| echo: false

library(here)
library(metafor)
library(dmetar)
library(psych)
library(grateful)
library(ggtext)
library(tidyverse)
library(extrafont)
library(rstatix)
library(ggbrace)


file_sources <- list.files(
  path = here::here("R"),
  pattern = "*.R"
)
source(here::here("R", file_sources[1]))
source(here::here("R", file_sources[2]))
```

CAUTION: I added the moderator variable last minute and didn't have a chance to check everything properly. 

# Introduction
The analysis follows the chapter [Fitting Three-Level Meta-Analysis Models in R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/multilevel-ma.html#multilevel-R) from the book [Doing Meta-Analysis in R](https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/), @harrer2021doing. 
```{r}
#| echo: false

cite_packages(output = "paragraph", out.dir = ".")
```

```{r results='asis'}
#| echo: false
summary_tables <- lapply(my_dat[1:3], function(x) {
  describeBy(x[, c("N", "es", "se_es")], skew = FALSE, group = x$drugType)
})

summary_tables[[4]] <- describe(my_dat[[4]][, c("N", "es", "se_es")], skew = FALSE)
names(summary_tables) <- file_sources
```

# Main analysis
Because some studies provide multiple values we use a three-level Meta-Analysis Model. The nested random effect gets assigned to the grouping variable "study". This means we allow the random intercept to vary across different studys. 
To obtain the estimated effect sizes for our two `drugType` levels I removed the intercept, as described in the documentation of the [metafor Package](https://www.metafor-project.org/doku.php/tips:models_with_or_without_intercept). 
Test statistics and confidence intervals for the fixed effects use a t-distribution.
The test of moderators checks the assumption that $\mu_{mdma} = \mu_{psych} = 0$, so we get a test for an overall effect of the variable `drugType`. 

```{r}
models <- lapply(my_dat[1:3], fit_rma.mv, mods = ~ drugType - 1)
```

To compare both `drugType` levels I defined a contrasts, testing if $\mu_{mdma} - \mu{psych} = 0$ (Wald-Type Test), see `?anova.rma`.
```{r}
drugType_contrasts <- fit_contrasts(models[1:3])
```

This is the same test done in a model with intercept for the regression weight of `drugTypepsychedelic`.  

```{r}
models_with_intercept <- lapply(my_dat[1:3], fit_rma.mv, mods = ~drugType)
# compare:
drugType_contrasts[[3]]
models_with_intercept[[3]]
```

Finally, we have one data set without the moderator variable: 
```{r}
## Without moderator for the last data set:
models[[4]] <- fit_rma.mv(df = my_dat[[4]])

names(models) <- names(my_dat)

## Get the summaries of all 4 models:
models_summary <- lapply(models, summary)
```

## $I^2$
How much heterogeneity is due to differences within studies (level 2), and how much due to between study-differences (level 3)? So are the effect sizes from the same study more similar than effect sizes from multiple studies?

```{r}
i2 <- lapply(models, var.comp)
```

## Results
### Attention
#### Descriptives
```{r}
#| echo: false

summary_tables[["20240115_MABerlin_attention.csv"]]
```

#### Model
```{r}
#| echo: false

models_summary[["20240115_MABerlin_attention.csv"]]

drugType_contrasts[["20240115_MABerlin_attention.csv"]]
```

#### $I^2$
```{r}
#| echo: false

i2[["20240115_MABerlin_attention.csv"]]
```

### Executive
#### Descriptives
```{r}
#| echo: false

summary_tables[["20240115_MABerlin_executive.csv"]]
```

#### Model
```{r}
#| echo: false

models_summary[["20240115_MABerlin_executive.csv"]]
drugType_contrasts[["20240115_MABerlin_executive.csv"]]
```

#### $I^2$
```{r}
#| echo: false

i2[["20240115_MABerlin_executive.csv"]]
```

### Memory
#### Descriptives
```{r}
#| echo: false

summary_tables[["20240115_MABerlin_memory.csv"]]
```

#### Model
```{r}
#| echo: false

models_summary[["20240115_MABerlin_memory.csv"]]
drugType_contrasts[["20240115_MABerlin_memory.csv"]]
```

#### $I^2$
```{r}
#| echo: false

i2[["20240115_MABerlin_memory.csv"]]
```

### Microdosing
#### Descriptives
```{r}
#| echo: false

summary_tables[["20240115_MABerlin_microdosing.csv"]]
```

#### Model
```{r}
#| echo: false

models_summary[["20240115_MABerlin_microdosing.csv"]]
```

#### $I^2$
```{r}
#| echo: false

i2[["20240115_MABerlin_microdosing.csv"]]
```

# Sensitivity analyses
In some cases reduntent predictors get dropped because there are not enogh cases with one of the predictors (e.g., sensitivity_psilocybin only inlcudes psychedelics).

```{r}
# Nonconvergence for this analysis, see: http://www.metafor-project.org/doku.php/tips:convergence_problems_rma_mv
my_dat[[3]] <- my_dat[[3]] %>% dplyr::select(-sensitivity_lsd)

sensitivity_analyses <- lapply(my_dat[1:3], fit_sensitivity, mods = ~ drugType - 1)
sensitivity_contrasts <- list()
sensitivity_contrasts[[1]] <- fit_contrasts(sensitivity_analyses[[1]][c("sensitivity_speed", "sensitivity_accuracy", "sensitivity_highestWeight", "sensitivity_highQuality")])
sensitivity_contrasts[[2]] <- fit_contrasts(sensitivity_analyses[[2]][c("sensitivity_speed", "sensitivity_accuracy", "sensitivity_highestWeight", "sensitivity_highQuality")])
sensitivity_contrasts[[3]] <- fit_contrasts(sensitivity_analyses[[3]][c("sensitivity_accuracy", "sensitivity_highestWeight", "sensitivity_highQuality")])

names(sensitivity_contrasts) <- names(sensitivity_analyses[1:3])

sensitivity_analyses[[4]] <- fit_sensitivity(my_dat[[4]])
names(sensitivity_analyses) <- names(my_dat)

sensitivity_summary <- lapply(sensitivity_analyses, function(domain) {
  lapply(domain, summary)
})
```


## Results

### Attention

#### Speed
```{r}
sensitivity_summary[["20240115_MABerlin_attention.csv"]]["sensitivity_speed"]
sensitivity_contrasts[["20240115_MABerlin_attention.csv"]]["sensitivity_speed"]
```

#### Accuracy
```{r}
sensitivity_summary[["20240115_MABerlin_attention.csv"]]["sensitivity_accuracy"]
sensitivity_contrasts[["20240115_MABerlin_attention.csv"]]["sensitivity_accuracy"]
```

#### Highest Weight
```{r}
sensitivity_summary[["20240115_MABerlin_attention.csv"]]["sensitivity_highestWeight"]
sensitivity_contrasts[["20240115_MABerlin_attention.csv"]]["sensitivity_highestWeight"]
```

#### Psilocybin
```{r}
sensitivity_summary[["20240115_MABerlin_attention.csv"]]["sensitivity_psilocybin"]
```

#### High Quality
```{r}
sensitivity_summary[["20240115_MABerlin_attention.csv"]]["sensitivity_highQuality"]
sensitivity_contrasts[["20240115_MABerlin_attention.csv"]]["sensitivity_highQuality"]
```

### Executive

#### Speed
```{r}
sensitivity_summary[["20240115_MABerlin_executive.csv"]]["sensitivity_speed"]
sensitivity_contrasts[["20240115_MABerlin_executive.csv"]]["sensitivity_speed"]
```

#### Accuracy
```{r}
sensitivity_summary[["20240115_MABerlin_executive.csv"]]["sensitivity_accuracy"]
sensitivity_contrasts[["20240115_MABerlin_executive.csv"]]["sensitivity_accuracy"]
```

#### Highest Weight
```{r}
sensitivity_summary[["20240115_MABerlin_executive.csv"]]["sensitivity_highestWeight"]
sensitivity_contrasts[["20240115_MABerlin_executive.csv"]]["sensitivity_highestWeight"]
```

#### Psilocybin
```{r}
sensitivity_summary[["20240115_MABerlin_executive.csv"]]["sensitivity_psilocybin"]
```

#### LSD
```{r}
sensitivity_summary[["20240115_MABerlin_executive.csv"]]["sensitivity_lsd"]
```

#### High Quality
```{r}
sensitivity_summary[["20240115_MABerlin_executive.csv"]]["sensitivity_highQuality"]
sensitivity_contrasts[["20240115_MABerlin_executive.csv"]]["sensitivity_highQuality"]
```

### Memory

#### Speed
```{r}
sensitivity_summary[["20240115_MABerlin_memory.csv"]]["sensitivity_speed"]
```

#### Accuracy
```{r}
sensitivity_summary[["20240115_MABerlin_memory.csv"]]["sensitivity_accuracy"]
sensitivity_contrasts[["20240115_MABerlin_memory.csv"]]["sensitivity_accuracy"]
```

#### Highest Weight
```{r}
sensitivity_summary[["20240115_MABerlin_memory.csv"]]["sensitivity_highestWeight"]
sensitivity_contrasts[["20240115_MABerlin_memory.csv"]]["sensitivity_highestWeight"]
```

#### Psilocybin
```{r}
sensitivity_summary[["20240115_MABerlin_memory.csv"]]["sensitivity_psilocybin"]
```

#### LSD
Did not converge.
```{r, eval = FALSE}
sensitivity_summary[["20240115_MABerlin_memory.csv"]]["sensitivity_lsd"]
```

#### High Quality
```{r}
sensitivity_summary[["20240115_MABerlin_memory.csv"]]["sensitivity_highQuality"]
sensitivity_contrasts[["20240115_MABerlin_memory.csv"]]["sensitivity_highQuality"]
```

### Microdosing
#### Highest Weight
```{r}
sensitivity_summary[["20240115_MABerlin_microdosing"]]["sensitivity_highestWeight"]
```

#### Psilocybin
```{r}
sensitivity_summary[["20240115_MABerlin_microdosing.csv"]]["sensitivity_psilocybin"]
```


# Interpretation

- `Variance Components`:
    * sigma^2.1 contains the level 3 between-cluster variance.
    * sigma^2.2 shows the variance within clusters (level 2).
- `Test of Moderators`: Indicates differences between the subgroups mdma & psychadelics.  
- `Model Results`
    * `estimate` is our estimated pooled effect. 
- `$I^2$`: 
    * $I^2$ quantifies the amount of variation not attributable to sampling error. In three level models, it is split into a part attributable to true effect size differences within clusters (level 2) and between cluster variation (level 3). 
We have 2 $I^2$ values per model quantifying the percentage of total variation associated with either level 2 or level 3. 

# Forest plots
```{r}
#| warning: false
#| message: false
#| echo: false

loadfonts(device = "win")

linecolour <- "black"
mdma_col <- "orange3"
psych_col <- "forestgreen"

my_dat[[4]]$drugType <- rep("psychedelic", nrow(my_dat[[4]]))

plot_dat_1 <- prep_dat(my_dat[[1]], background_stripes = c(rep(c("grey90", "white"), 8), "grey90"))
plot_dat_2 <- prep_dat(my_dat[[2]], background_stripes = c(rep(c("grey90", "white"), 9), "grey90"))
plot_dat_3 <- prep_dat(my_dat[[3]], background_stripes = rep(c("grey90", "white"), 14))
plot_dat_4 <- prep_dat(my_dat[[4]], background_stripes = rep(c("grey90", "white"), 3))


diamond <- function(side_length, center_x, center_y, ci_ub, ci_lb) {
  base <- data.frame(
    x_coords = c(ci_ub, center_x, ci_lb, center_x),
    y_coords = c(0, 0.25, 0, -0.25) + center_y
  )
  return(base)
}

max_range <- range(c(
  min(plot_dat_1$ci_lb, na.rm = TRUE), max(plot_dat_1$ci_ub, na.rm = TRUE),
  min(plot_dat_2$ci_lb, na.rm = TRUE), max(plot_dat_2$ci_ub, na.rm = TRUE),
  min(plot_dat_3$ci_lb, na.rm = TRUE), max(plot_dat_3$ci_ub, na.rm = TRUE)
))

p_attention <- plot_forestplot(plot_dat_1,
  scale_min = -8.123048,
  scale_max = 3.263000,
  model_obj = models[[1]],
  contrast = drugType_contrasts[[1]],
  i2 = i2[[1]],
  model_res = data.frame(
    estimate = models[[1]]$beta,
    ci_lb = models[[1]]$ci.lb,
    ci_ub = models[[1]]$ci.ub,
    drugType = c("MDMA", "Psychedelic")
  )
)

p_executive <- plot_forestplot(plot_dat_2,
  scale_min = -8.123048, scale_max = 3.263000,
  model_obj = models[[2]],
  contrast = drugType_contrasts[[2]],
  i2 = i2[[2]],
  model_res = data.frame(
    estimate = models[[2]]$beta,
    ci_lb = models[[2]]$ci.lb,
    ci_ub = models[[2]]$ci.ub,
    drugType = c("MDMA", "Psychedelic")
  )
)
p_memory <- plot_forestplot(plot_dat_3,
  scale_min = -8.123048, scale_max = 3.263000,
  model_obj = models[[3]],
  contrast = drugType_contrasts[[3]],
  i2 = i2[[3]],
  model_res = data.frame(
    estimate = models[[3]]$beta,
    ci_lb = models[[3]]$ci.lb,
    ci_ub = models[[3]]$ci.ub,
    drugType = c("MDMA", "Psychedelic")
  )
)

p_microdosing <- plot_forestplot(plot_dat_4,
  scale_min = -8.123048, scale_max = 3.263000,
  model_obj = models[[4]],
  i2 = i2[[4]],
  model_res = data.frame(
    estimate = models[[4]]$beta,
    ci_lb = models[[4]]$ci.lb,
    ci_ub = models[[4]]$ci.ub,
    drugType = c("MDMA", "Psychedelic")
  )
)

# ggsave("p1_tiff.tiff", units = "cm", width = 32, height = 24)
# dev.off()
```

```{r eval = FALSE}
save_plot(p_memory, "p_memory.pdf")
save_plot(p_attention, "p_attention.pdf", height = 255 * (nrow(my_dat[["20240115_MABerlin_attention.csv"]])) /
  (nrow(my_dat[["20240115_MABerlin_memory.csv"]])) + 40)
save_plot(p_executive, "p_executive.pdf", height = 255 * (nrow(my_dat[["20240115_MABerlin_executive.csv"]])) /
  (nrow(my_dat[["20240115_MABerlin_memory.csv"]])) + 40)
save_plot(p_microdosing, "p_microdosing.pdf",
  height = 255 * (nrow(my_dat[["20240115_MABerlin_microdosing.csv"]])) /
    (nrow(my_dat[["20240115_MABerlin_memory.csv"]])) + 40
)
```


# References
